О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-27 pps-linear-bound/pps-linear-lower-bound.tex
bisector -> perpendicular bisector

\begin{definition}
	A \textit{cross} for points $M_1$ and $M_2$, denoted by $cr(M_1,M_2)$, is the union of two straight lines:
	the line which the points $M_1$ and $M_2$ are situated on,
	and the bisector of line segment $M_1 M_2$.
\end{definition}

@@

\begin{definition}
	For a line segment $M_1 M_2$ and an integer $k$, $-|M_1 M_2| < k < |M_1 M_2|$,
	we define a $\rho(k,M_1 M_2)$-curve as the set of points $N$
	for which the equality $|N M_1| - |N M_2| = k$ holds.
\end{definition}
So, in the planar case a $\rho(k,M_1 M_2)$-curve
is a branch of a hyperbola for $k\neq 0$ and the bisector of line segment $M_1 M_2$ for $k=0$.

@@

\begin{proof}
	Let $m$ denote the bisector of line segment $M_1 M_2$.
	Due to the triangle inequality, there are two possibilities to place each of points $M_i$, $i=3,4$:

@@

	And vice versa, if $M$ is a planar integral point set of $n$ points
	such that for some $M_1,M_2 \in M$ equality $|M_1 M_2|=1$ holds,
	then $M$ consists of $n-1$ points, including $M_1$ and $M_2$, on a straight line,
	and one point out of the line, on the bisector of line segment $M_1 M_2$.
	There is only one maximal integral point set $M' \supseteq M$,
	and the bisector is the axis of symmetry for $M'$.
	Moreover, if $n > 3$, then the distance 1 occurs in $M$ (and $M'$) only once.
\end{theorem}

>>>>

\begin{definition}
	A \textit{cross} for points $M_1$ and $M_2$, denoted by $cr(M_1,M_2)$, is the union of two straight lines:
	the line through $M_1$ and $M_2$,
	and the perpendicular bisector of line segment $M_1 M_2$.
\end{definition}

@@

\begin{definition}
	For a line segment $M_1 M_2$ and an integer $k$, $-|M_1 M_2| < k < |M_1 M_2|$,
	we define a $\rho(k,M_1 M_2)$-curve as the set of points $N$
	for which the equality $|N M_1| - |N M_2| = k$ holds.
\end{definition}
So, in the planar case a $\rho(k,M_1 M_2)$-curve
is a branch of a hyperbola for $k\neq 0$ and the perpendicular bisector of line segment $M_1 M_2$ for $k=0$.

@@

\begin{proof}
	Let $m$ denote the perpendicular bisector of line segment $M_1 M_2$.
	Due to the triangle inequality, there are two possibilities to place each of points $M_i$, $i=3,4$:

@@

	And vice versa, if $M$ is a planar integral point set of $n$ points
	such that for some $M_1,M_2 \in M$ equality $|M_1 M_2|=1$ holds,
	then $M$ consists of $n-1$ points, including $M_1$ and $M_2$, on a straight line,
	and one point out of the line, on the perpendicular bisector of line segment $M_1 M_2$.
	There is only one maximal integral point set $M' \supseteq M$,
	and the perpendicular bisector is the axis of symmetry for $M'$.
	Moreover, if $n > 3$, then the distance 1 occurs in $M$ (and $M'$) only once.
\end{theorem}
